Supplementary Materials to ``Statistical paradoxes in coronavirus case-counts: selection bias, measurement error, and the COVID-19 pandemic''

### 2022-02-18 write-up/covid-supplement-writeup.tex
Update covid-supplement-writeup.tex

\begin{figure}[!th]
 \centering
 \includegraphics[width=.9\linewidth]{../figs/tv_air_cis.png}
 \caption{IPW2 estimate with confidence intervals}
 \label{fig:air_cis}
\end{figure}

@@

\begin{figure}[!th]
 \centering
 \includegraphics[width=.7\linewidth]{../figs/undercounting.png}
 \caption{Undercount based on SEIR model}
 \label{fig:undercounting}
\end{figure}

>>>>

\begin{figure}[!th]
 \centering
 \includegraphics[width=.6\linewidth]{../figs/tv_air_cis.png}
 \caption{IPW2 estimate with confidence intervals}
 \label{fig:air_cis}
\end{figure}

@@

\begin{figure}[!th]
 \centering
 \includegraphics[width=.6\linewidth]{../figs/undercounting.png}
 \caption{Undercount based on SEIR model}
 \label{fig:undercounting}
\end{figure}

\section{Alternative estimator }
\label{app:cori_rt}

\begin{figure}
 \centering
  \includegraphics[width=.9\linewidth]{../figs/seir_cori_rt.png}
  \caption{Effective reproductive rate estimator}
  \label{fig:r-bias}
 \caption{Potential bias in instantaneous reproductive rate estimator based on~\cite{Cori20113} under an SEIR model with $\beta = 1.2$, $\gamma = 0.15$, and $\sigma = 0.3$.  Here, $f = 0.02$, $FP = 0.024$, $FN = 0.13$, and a range of relative sampling fractions $M = f_1/f_0$ are considered.}
 \label{fig:rates}
 \end{figure}
